---
title: "Students' Dropout and Population in Primary Age Group"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

```{r setup, include=FALSE}
library("ggplot2")
library("shiny")
library("maptools")
library("scales")
library("RColorBrewer")
library("tidyverse")
library("flexdashboard")
library("plotrix")
library("sf")
library("tmap")
library("tmaptools")
library("leaflet")
library("dplyr")
library("plotly")

options(scipen = 999)
mymap=st_read("C:/Users/dawns/AppData/Roaming/SPB_Data/DataVis_Project/maps-master/States/Admin2.shp",stringsAsFactors=FALSE)
pop_data=read.csv("C:/Users/dawns/Downloads/actual_pop.csv")
map_and_pop=inner_join(mymap,pop_data)

general=read.csv("C:/Users/dawns/Downloads/enrollment_general.csv")
sc=read.csv("C:/Users/dawns/Downloads/enrollment_sc.csv")
st=read.csv("C:/Users/dawns/Downloads/enrollment_st.csv")
enr_total=data.frame(Year=general$Year,General=general$Total,SC=sc$Total,ST=st$Total)

drop_data=read.csv("C:/Users/dawns/Downloads/droupout.csv")
legends=drop_data$Category
tot=sum(drop_data$Total)
avg=tot/length(drop_data$Total)
total=round((drop_data$Total/tot)*100,2)
gen_tot=drop_data$Boys[1]+drop_data$Girls[1]
sc_tot=drop_data$Boys[2]+drop_data$Girls[2]
st_tot=drop_data$Boys[3]+drop_data$Girls[3]
gen_gender=c((drop_data$Boys[1]/gen_tot)*100,(drop_data$Girls[1]/gen_tot)*100)
sc_gender=c((drop_data$Boys[2]/sc_tot)*100,(drop_data$Girls[2]/sc_tot)*100)
st_gender=c((drop_data$Boys[3]/st_tot)*100,(drop_data$Girls[3]/st_tot)*100)

enr_12_14=round(c(general$Male[8]/general$Female[8],general$Male[9]/general$Female[9],general$Male[10]/general$Female[10]),2)
drop_12_14=c(5.62,4.67,4.34)
enr_drp=data.frame(Category=general$Year[8:10],Enrollment=enr_12_14,Dropout=drop_12_14)
```

## Column {data-width=200}
### **General** Category Droupout
```{r}
valueBox(drop_data$Total[1],icon="fa-arrow-alt-circle-down",color="green")

```

### **Scheduled Caste** Category Droupout
```{r}
valueBox(drop_data$Total[2],icon="fa-arrow-alt-circle-down",color="blue")

```

### **Scheduled Tribe** Category Droupout
```{r}
valueBox(drop_data$Total[3],icon="fa-arrow-alt-circle-down",color="red")

```

## Column {data-width=300 .tabset}
### General
```{r}
pie3D(gen_gender,labels=c(drop_data$Boys[1],drop_data$Girls[1]),col=brewer.pal(2,"Set1"),clockwise = TRUE,explode = 0.1)
legend("topright",c("Boys","Girls"),fill=brewer.pal(2,"Set1"))

```

### Scheduled Castes
```{r}
pie3D(sc_gender,labels=c(drop_data$Boys[2],drop_data$Girls[2]),col=brewer.pal(2,"Set1"),clockwise = TRUE,explode = 0.1)
legend("topright",c("Boys","Girls"),fill=brewer.pal(2,"Set1"))

```

### Scheduled Tribes
```{r}
pie3D(st_gender,labels=c(drop_data$Boys[3],drop_data$Girls[3]),col=brewer.pal(2,"Set1"),clockwise = TRUE,explode = 0.1)
legend("topright",c("Boys","Girls"),fill=brewer.pal(2,"Set1"))

```


## Column{data-width=300}
### **Correlation** between Student Enrollment & Dropout for 2012-2014
```{r}
cor.test(enr_drp$Enrollment,enr_drp$Dropout)
```

### Inference
A correlation value of 0.2(~0) suggests that although Student Dropout rate and Enrollment rate have positive correlation, it's not significant enough to be influential on each other

## Row {data-width=300}
### State-wise Population of children in **6-10** age group 

```{r}
tm_shape(map_and_pop)+tm_polygons("Total.Population",id="ST_NM")+tm_text("ST_NM",size="AREA",root=5)
tmap_mode("view")
tmap_last()

```